### 2014-05-16 brains-protocol.tex
Figure updates
* Replace timebag evolution figure
* Cosmetic changes in substitution chains pedagogical figure
No need for '!' in placing figure
Rework section 4
* It properly explains why the substitution detection model is extended
* It explains the final figure for substitution detection

\subsection{Temporal binning}

@@

@@

\begin{figure*}[!tbh]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/timebags_evolution_recursive_min20_no-exclusion.png}
    \caption{\textbf{Feature distribution evolution:} evolution of the distribution of feature values in substitution chains over successive 2-day time bags (bags 0 to 18, i.e. days 0 to 37).
    The legends indicate the number of words left in each time bag; these decrease exponentially since only a fraction of the quotes undergo substitution at each step.
    After a period of time, each feature becomes concentrated in a specific range of its own.}
    \label{fig:timebags-evolution}
\end{figure*}

@@

We then focus on the individual substitution process at work when authors transform quotations, by examining the features of the substituted and substituting words in each substitution.
Note that since we only consider substitutions and not faithful copies, we measure the features of an alteration \emph{knowing that there has been an alteration}, and we do not take invariant quotations into account.
Indeed, in the first case we know there has been a human reformulation, whereas in the second case it is impossible to know whether there has been perfect human reformulation or simply digital copy-pasting of a source (``{\sc Ctrl-C}/{\sc Ctrl-V}'').

\TB{This model has two main effects.
First, the binning influences how many times quote occurrences can be counted as substitutions: in Figure~\ref{fig:substitution-temporal-binning-b}, occurrences of $q_b$ on the 21st and 22nd are counted as substitutions, whereas the occurrence on the 23rd is not.
Second, the ``majority'' rule defines how quotes are sourced in substitutions: in the third drawing on Figure~\ref{fig:substitution-temporal-binning}, $q_b$ holds the majority and is the considered the basis for the last occurrence of $q_a$, in spite of $q_a$ having appeared earlier at the very beginning (indeed in the situation shown in Figure~\ref{fig:substitution-temporal-binning}, this seems to be the most likely scenario).}

\TB{\textbf{Source quotes} in the source interval for substitutions can be further restricted, e.g. to only the most frequent quote in the interval as in the model described above,}

@@

We build two main observables for each word feature.
First, we measure the susceptibility for words to be the source of a substitution, knowing that there has been a variation, in order to show which semantic features are the most likely to attract a substitution under this condition.
Second, we measure the variation of word feature over a substitution, looking at the variation of a given feature between start and arrival words.

@@

We also considered an alternative null hypothesis, denoted $\mathcal{H}_{00}$, where the arrival word is chosen randomly \emph{among immediate synonyms of the start word}, i.e. an arrival word chosen among semantically plausible though still random words.
\footnote{In this case $\warrival_{00}$ does depend on $\wstart$.} \rk{Do we present these results?}\cam{nope}\rk{S: Then we must say the results are the same.}

>>>>

\subsection{Temporal binning}
\label{sec:temporal-binning}

@@

\begin{figure*}[th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/timebags_evolution_recursive_min20_no-exclusion.png}
    \caption{\textbf{Feature distribution evolution:} evolution of the distribution of feature values in substitution chains over successive 2-day time bags (bags 0 to 18, i.e. days 0 to 37).
    The legends indicate the number of words left in each time bag; these decrease exponentially since only a fraction of the quotes undergo substitution at each step.
    After a period of time, each feature becomes concentrated in a specific range of its own.}
    \label{fig:timebags-evolution}
\end{figure*}

@@

@@

We then focus on the individual substitution process at work when authors transform quotations, by examining the features of the substituted and substituting words in each substitution.

To do so we first extend the substitution detection model used in the previous section to reduce possible false positives.
Indeed, when in the previous section we were forced to detect substitutions with a very permissive model to make sure chains of substitutions could be extracted (at the expense of possible false positives, the only effect of this being additional noise in the results, making our conclusions more conservative), here we can afford to detect substitutions more precisely.
We thus add the constraint that substitutions can only stem from the most frequent quote in the preceding time bag.
Since it is fairly certain that authors will have come upon the most frequent quote in any given time bag (\emph{v.} all the other quotes in that time bag), restricting substitutions to the most frequent quote makes sure we only detect substitutions that really occurred, greatly reducing the number of false positives.

Let us illustrate this ``majority'' rule by going back to the example described in Section~\ref{sec:temporal-binning} and extending it, in Figure~\ref{fig:substitution-q_max}.
In time bag~3, $q_b$ now holds the majority and is considered the unique basis for the last occurrence of $q_a$ (in time bag~4).
This is despite the fact that $q_a$ also appears in time bag~3 alongside $q_b$, and despite it having appeared earlier at the very beginning of the quotation family (indeed in the situation shown in Figure~\ref{fig:substitution-q_max}, this seems to be the most likely scenario).
Conversely, if $q_a$ had been the most frequent quote in time bag 3, the last occurrence of $q_a$ in time bag~4 would have been considered a faithful copy of the occurrence in time bag~3.

@@

With the substitution detection model thus refined, we build two main observables for each word feature.
First, we measure the susceptibility for words to be the source of a substitution, knowing that there has been a variation, in order to show which semantic features are the most likely to attract a substitution under this condition.
Second, we measure the variation of word feature over a substitution, looking at the variation of a given feature between start and arrival words.

Note that since we only consider substitutions and not faithful copies, we measure the features of an alteration \emph{knowing that there has been an alteration}, and we do not take invariant quotations into account.
Indeed, in the first case we know there has been a human reformulation, whereas in the second case it is impossible to know whether there has been perfect human reformulation or simply digital copy-pasting of a source (``{\sc Ctrl-C}/{\sc Ctrl-V}'').

@@

We also considered an alternative null hypothesis, denoted $\mathcal{H}_{00}$, where the arrival word is chosen randomly \emph{among immediate synonyms of the start word}, i.e. an arrival word chosen among semantically plausible though still random words.\footnote{In this case $\warrival_{00}$ does depend on $\wstart$.}
The results were not qualitatively changed with this second null hypothesis, so for the sake of clarity we chose to present the results using the simpler~$\mathcal{H}_0$.
